DLISA: Distributed Learning-based \\ Intelligent Service Agents

### 2014-11-28 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask. However, in our model, our community would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

@@

@@

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $64$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DLISA Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

@@

\begin{table}[h]
\begin{tabular}{|c|c|}
\hline
 Method&Miss\\ \hline
 DLISA r=0.05& 375 \\ \hline
 DLISA r=0.07& 137 \\ \hline
 DLISA r=0.10& 6 \\ \hline
 DLISA r=0.20& 6 \\ \hline
Rational Method& 717 \\ \hline
Greedy Method& 828 \\ \hline
\end{tabular}
\caption{Number of communities that misses the optimal decision, out of 1,000 communities}
\label{fail_rate}
\end{table}

>>>>

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask. However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -3.851432 & - & 6.969072 & -3.851432 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

@@

Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations. Each row shows the gain the community can achieve by collaborating with other 5 communities. In this example for community $\textless 348 \textgreater$ we have: \\
$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and would contain community $\{\textless1934, 2117\textgreater\}$.

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $T$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DLISA Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

@@

\begin{table}[ht]
\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
\centering % used for centering table
\begin{tabular}{|c|c|} % centered columns (4 columns)
\hline %inserts double horizontal lines
 Method&Miss \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
 DLISA r=0.05& 375 \\ % inserting body of the table
 DLISA r=0.07& 137 \\
 DLISA r=0.10& 6 \\
 DLISA r=0.20& 6 \\
Rational Method& 717 \\
Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{fail_rate} % is used to refer this table in the text
\end{table}
